Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-11-04 theory.tex
Correcting alpha/beta definitions
Adding interim definitions to beta equation

\begin{subequations}
    \label{eq_alphabeta}
    \begin{equation} \label{eq_alpha_def}
        \alpha = \frac{N}{1-N}\frac{1-N'}{N'}
    \end{equation}
    \begin{equation}\label{eq_beta-def}
        \beta = \frac{N''}{1-N''}\frac{1-N}{N}
    \end{equation}
    \begin{equation}\label{eq_gamma-def}
        \gamma = \alpha.\beta
    \end{equation}
\end{subequations}

@@

From mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
\eqref{eq_alphabeta} it is possible to express $\beta$ as a function of the
feed abundance, $R$, the cut $\theta$ and $\alpha$:

\begin{equation}\label{eq_beta}
    \beta =   R \left(\dfrac{1-\theta}
                     {\dfrac{R}{R+1}- \theta \dfrac{\alpha R}{1+\alpha R}} -1\right)
\end{equation}

>>>>

\begin{subequations}
    \label{eq_alphabeta}
    \begin{equation} \label{eq_alpha_def}
        \alpha = \frac{1-N}{N}\frac{N'}{1-N'}
    \end{equation}
    \begin{equation}\label{eq_beta-def}
        \beta = \frac{1-N''}{N''}\frac{N}{1-N}
    \end{equation}
    \begin{equation}\label{eq_gamma-def}
        \gamma = \alpha.\beta
    \end{equation}
\end{subequations}

@@

From equations \eqref{eq_alphabeta}, the product assay can be expressed as:

\begin{equation}\label{eq_product_assay}
    N' = \frac{\alpha R}{1 + \alpha R}
\end {equation}

Then, from mass conservation, $N = \theta N' + (1-\theta)N''$, equation
\eqref{eq_product_assay}, and the definition of the abundance, $R$, it is
possible to express $\beta$ as a function of only the feed abundance,
$R$, the cut $\theta$ and $\alpha$:

\begin{subequations}
    \begin{equation}\label{eq_beta_interim}
        \beta = \left( 1 - \frac{N - \theta N'}{1-\theta} \right)
                        \left( \frac{R}{\frac{N - \theta N'}{1 - \theta}} \right)
    \end{equation}
    \begin{equation}\label{eq_beta}
        \beta =   R \left(\dfrac{1-\theta}
                        {\dfrac{R}{R+1}- \theta \dfrac{\alpha R}{1+\alpha R}} -1\right)
    \end{equation}
\end{subequations}
